Parameters estimation via HOSVD

### 2025-01-09 Code/R/Research/HOSVD parameters estimate.Rmd
Numerical tests

    for (d in seq_along(est.dims)) {
      par.tssa <- tens_esprit(x,
                              I,
                              L,
                              groups = groups,
                              est_dim = d,
                              decomp = "HOSVD",
                              status = FALSE)

@@

close(pb)
beep()
save(
  rate1.rrmse,
  rate2.rrmse,
  freq1.rrmse,
  freq2.rrmse,
  file = paste0("./Research/comp_results/dim_rrmse", plot.name, "_tens.RData")
)
```

>>>>

    for (d in seq_along(est.dims)) {
      par.tssa <- tens_esprit(x,
                              I,
                              L,
                              groups = groups,
                              est_dim = d,
                              decomp = "HOSVD",
                              status = FALSE)
      if (any(par.tssa[[1]]$frequencies < 0))
        stop("Negative frequency")
      pars.tssa[[d]]$rate1[i] <- max(par.tssa[[1]]$rates[1], par.tssa[[1]]$rates[2])
      pars.tssa[[d]]$rate2[i] <- min(par.tssa[[1]]$rates[1], par.tssa[[1]]$rates[2])
      pars.tssa[[d]]$freq1[i] <- min(par.tssa[[1]]$frequencies[1], par.tssa[[1]]$frequencies[2])
      pars.tssa[[d]]$freq2[i] <- max(par.tssa[[1]]$frequencies[1], par.tssa[[1]]$frequencies[2])
    }
    setTxtProgressBar(pb, (j - 1) * R + i)
  }

@@

close(pb)
beep()
# save(
#   rate1.rrmse,
#   rate2.rrmse,
#   freq1.rrmse,
#   freq2.rrmse,
#   file = paste0("./Research/comp_results/dim_rrmse", plot.name, "_tens.RData")
# )
```
